---
title: "Using nomnoml with pdf documents"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Using nomnoml with pdf documents}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(nomnoml)
```


You can use `nomnoml` chunks in R Markdown with PDF output.  Here is an example R Markdown, including the yaml header.  Notice that you can use `{nomnoml}` chunks and these will be rendered by the `nomnoml` engine.

````markdown
---
title: "A Diagram"
output: html_document
---

`r ''````{r, setup, include=FALSE}
library(nomnoml)
```

`r ''````{nomnoml}
#stroke: orange
#.box: fill=#8f8 dashed visual=ellipse

[A]-[B]
[B]-[<box>C]
```
````

## Chunk examples

Here is a rendered example of a chunk, using the default plot size:


```{nomnoml, svg=FALSE}
#stroke: #a86128
#direction: down
[<frame>Decorator pattern|
  [<abstract>Component||+ operation()]
  [Client] depends --> [Component]
  [Decorator|- next: Component]
  [Decorator] decorates -- [ConcreteComponent]
  [Component] <:- [Decorator]
  [Component] <:- [ConcreteComponent]
]
```


And the same diagram, this time with specified size:

```{nomnoml, svg=TRUE, width="2in", height="2in"}
#stroke: #a86128
#direction: down
[<frame>Decorator pattern|
  [<abstract>Component||+ operation()]
  [Client] depends --> [Component]
  [Decorator|- next: Component]
  [Decorator] decorates -- [ConcreteComponent]
  [Component] <:- [Decorator]
  [Component] <:- [ConcreteComponent]
]
```

